Inference for multivariate peaks over threshold models

### 2021-10-12 results.tex
update

\section{Data illustrations}

\subsection{Simulations}
We have introduced this projected gamma distribution existing on $\mathcal{S}_{\infty}^{p-1}$.  As a
  means of evaluating how well we can recover a distribution under the proposed model, we have
  generated a series of datasets on $\mathcal{S}_{\infty}^{d-1}$, for $d$ ranging between 3 and 20.
  We generated each dataset from a mixture of projected Gammas, with the number of mixture components
  ranging between 3 and 12.  The generation procedure is detailed in Algorithm~\ref{algo:simulated}.
  \begin{algorithm}[htb]
    \For{$n_{\text{mix}}$ in $[3, 6, 9, 12]$}{
      Generate $n_{\text{mix}} \times 20$ shape Parameters $\alpha$\\
      Generate $n_{\text{mix}} \times 20$ Rate Parameters $\beta$\\
      Generate $500$ Mixture Component Identifiers $\delta$\\
      \For{$i$ in $1,\ldots,500$}{
        Generate ${\bf X}_i \sim \prod_{\ell = 1}^d\text{Ga}\left(X_{il}\mid\alpha_{\delta_i,l},\beta_{\delta_i, l}\right)$
        }
      \For{$n_{\text{col}}$ in $[3,6,12,20]$}{
        Project columns 1 to $n_{\text{col}}$ of ${\bf X}$ onto $\mathcal{S}_{\infty}^{n_{\text{col}} - 1}$ and save.
        }
    }
    \caption{Simulated Angular Dataset Generation Routine\label{algo:simulated}}
  \end{algorithm}
  The choice of generation routine for $\alpha = \alpha_0 + \alpha_1$ where
  $\alpha_0 \sim \text{Unif}(\alpha_0\mid 0,4)$, $\alpha_1\sim \text{Gamma}(\alpha_1\mid 1,1)$.
  The choice of generation routine for $\beta$ is $\beta\sim\text{Unif}(\beta\mid 0.25, 2.5)$.
  This choice was made to ensure that $\beta$ does not approach 0 in the generation routine.

@@

\subsection{Integrated Vapor Transport}
One metric by which we might identify and declare atmospheric rivers is the integrated water vapor
  transport, or \emph{IVT}.  This value represents the total amount of water
  vapor being transported in an atmospheric column---that is, a column of the troposphere above a given
  area of the surface of the Earth. Raw data are measured by dropsondes---measurement devices dropped
  out of aircraft, taking measurements as they fall to the earth.~\citep{ralph2017}  A data vector
  includes an estimate of IVT at grid cell at a period in time; where a grid cell specifies the surface
  of the earth under the atmospheric column.  We have two such datasets, in differing spatial
  resolutions---the lower resolution data splits the coast of california into 8 grid cells, while the
  higher resolution does so into 47 grid cells~\citep{guan2015}.

>>>>

\section{Data illustrations\label{sec:results}}

\subsection{Simulations\label{subsec:simulated}}
We have introduced this projected gamma distribution existing on $\mathcal{S}_{\infty}^{p-1}$.  As a
  means of evaluating how well we can recover a distribution under the proposed model, we have
  generated a series of datasets on $\mathcal{S}_{\infty}^{d-1}$, for $d$ ranging between 3 and 20.
  We generated each dataset from a mixture of projected Gammas, with the number of mixture components
  ranging between 3 and 12.  The generation procedure is detailed in Algorithm~\ref{algo:simulated}.
  \begin{algorithm}[htb]
    \For{$n_{\text{mix}}$ in $[3, 6, 9, 12]$}{
      Generate $n_{\text{mix}} \times 20$ shape Parameters $\alpha$\\
      Generate $n_{\text{mix}} \times 20$ Rate Parameters $\beta$\\
      Generate $500$ Mixture Component Identifiers $\delta$\\
      \For{$i$ in $1,\ldots,500$}{
        Generate ${\bf X}_i \sim \prod_{\ell = 1}^d\text{Ga}\left(X_{il}\mid\alpha_{\delta_i,l},\beta_{\delta_i, l}\right)$
        }
      \For{$n_{\text{col}}$ in $[3,6,12,20]$}{
        Project columns 1 to $n_{\text{col}}$ of ${\bf X}$ onto $\mathcal{S}_{\infty}^{n_{\text{col}} - 1}$ and save.
        }
    }
    \caption{Simulated Angular Dataset Generation Routine\label{algo:simulated}}
  \end{algorithm}
  The choice of generation routine for $\alpha = \alpha_0 + \alpha_1$ where
  $\alpha_0 \sim \text{Unif}(\alpha_0\mid 0,4)$, $\alpha_1\sim \text{Gamma}(\alpha_1\mid 1,1)$.
  The choice of generation routine for $\beta$ is $\beta\sim\text{Unif}(\beta\mid 0.25, 2.5)$.
  This choice was made to ensure that $\beta$ does not approach 0 in the generation routine.

@@

\subsection{Integrated Vapor Transport\label{subsec:ivt}}
One metric by which we might identify and declare atmospheric rivers is the integrated water vapor
  transport, or \emph{IVT}.  This value represents the total amount of water
  vapor being transported in an atmospheric column---that is, a column of the troposphere above a given
  area of the surface of the Earth. Raw data are measured by dropsondes---measurement devices dropped
  out of aircraft, taking measurements as they fall to the earth.~\citep{ralph2017}  A data vector
  includes an estimate of IVT at grid cell at a period in time; where a grid cell specifies the surface
  of the earth under the atmospheric column.  We have two such datasets, in differing spatial
  resolutions---the lower resolution data splits the coast of california into 8 grid cells, while the
  higher resolution does so into 47 grid cells~\citep{guan2015}.
